Model

### 2019-05-31 stats/model.Rmd
plot sem know params across model runs

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 8,
  cores = 8,
  inference_opts = list(method = "incrementalMH", 
                        samples = 4000, 
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

@@

plot_sem_know <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = me_model_data$familiar), .) %>%
  mutate(sem_know = plogis(int + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

@@

>>>>

# sem_know_model<- webppl(
#   program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
#   data = list(data = me_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 8,
#   cores = 8,
#   inference_opts = list(method = "incrementalMH", 
#                         samples = 4000, 
#                         burn = 2000,
#                         verbose = T,
#                         lag = 1,
#                         verboseLag = 1000)
# )

@@

plot_sem_know <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know = plogis(int + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

@@

### Comparing sem knowledge parameters between model runs

# 3 chains, 6000 iterations per chain, 2000 burn in, lag = 1
sem_know_run_1 <- readRDS("../saves/sem_know_model.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "1")

# 8 chains, 4000 iterations per chain, 2000 burn in, lag = 1
sem_know_run_2 <- readRDS("../saves/sem_know_model_2.rds")%>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  mutate(run = "2")

sem_know_run_iteration <- bind_rows(
   sem_know_run_1,
   sem_know_run_2)

sem_know_run_summary <- sem_know_run_iteration%>%
  group_by(run,item)%>%
  summarise(overall_int = estimate_mode(int),
            overall_slope = estimate_mode(slope))

sem_know_run <- sem_know_run_iteration %>%
  left_join(sem_know_run_summary)

run_comp <- sem_know_run %>%
  left_join(expand.grid(
      age = unique(me_model_data$age),
      item = unique(me_model_data$familiar)), .) %>%
  mutate(sem_know_ci = plogis(int + slope * age),
         sem_know = plogis(overall_int + overall_slope * age)) %>%
  group_by(run,item, age) %>%
  summarise(sem_know = estimate_mode(sem_know), 
            sem_know_uci = hdi_upper(sem_know_ci),
            sem_know_lci = hdi_lower(sem_know_ci))

ggplot(run_comp, aes(x = age+2, y= sem_know, fill = run))+
  geom_line(size = 1, aes(col = run))+
  geom_ribbon(aes(ymin=sem_know_lci, ymax = sem_know_uci), alpha = .2)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  facet_wrap(~item)+
  theme_few()+
  scale_colour_solarized()+
  scale_fill_solarized()
```
